Exploring Determinants of Child Mortality Globally (2022): The Role of Vaccination, Healthcare Spending, and Nutrition

### 2025-04-15 paper/paper.qmd
Result

>>>>

The focal loss is specified as follows: 
$$
FL(p_t) = -\alpha_t (1-p_t)^\gamma \log(p_t)
$$
Here $p_t$ is the model's predicted probility if the true label is strong lensing, one minus the predicted probbility if the true label is not strong lenseing. $a_t$ is 0.75 if the true lavel is strong lensing and 0.25 if the true label is not strong lensing. The aim of this loss function is to avoid easy labels and penalize the model most if it incorrectly label a strong lensing one as non-lensing.

## New evaluating matrics

Despite the fact that we need new loss functions, we also need new evaluation metrics to better evaluate the performance of model on biased labels. As said, the labels of strong is very rare relative to non lensing. So if we use the default prediction accuracy then by just predicting everything by strong lensing the model will get a very decent performance while did not contribute much to the final goal of our research purpose.

Thus we will propose a practical and better to understand metric, which is the # of correct labels in the top 10% of the highest ranked data. This is more to common sense and align the final purpose of our research.

# Results
